---
title: "Untitled"
author: "Nikos Patias"
date: "10/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, include=FALSE}
library(sf)

# 1. Read in the FUA grids
FUAs <- st_read("../data/layers/grids.gpkg")

# if we want we can subset the dataset only to the FUA that we are interested
FUAs <- subset(FUAs, fuaname %in% c("London","Manchester",
                                    "West Midlands urban area","Leeds",
                                    "Glasgow","Liverpool",
                                    "Southampton","Newcastle upon Tyne",
                                    "Nottingham","Sheffield",
                                    "Bristol","Edinburgh"))

# use Birmingham as it is easier to report
FUAs$fuaname[FUAs$fuaname == "West Midlands urban area"] <- "Birmingham"


```



## read the data
```{r}

# Read all the RDS files with gridded data
data_2001 <- readRDS(file = "../data/gridded_data/full_data_2001.Rds")
data_2006 <- readRDS(file = "../data/gridded_data/full_data_2006.Rds")
data_2011 <- readRDS(file = "../data/gridded_data/full_data_2011.Rds")
data_2016 <- readRDS(file = "../data/gridded_data/full_data_2016.Rds")

# treat the dataset as dataframe
st_geometry(data_2001) <- NULL
st_geometry(data_2006) <- NULL
st_geometry(data_2011) <- NULL
st_geometry(data_2016) <- NULL



# source the functions for composite index function
source('Composite_index_function.R')

# source the functions for creating plots
source('plot_functions.R')

# source for helper functions
source('helpers.R')

library(dplyr)
library(psych)
library(tidyr) # this is used for drop_na()
library(RColorBrewer)
library(leaflet)
library(leaflet.extras)

# run the composite index function
CI_2001 <- Comp_ind(data_2001, FUAs, "2001")
CI_2006 <- Comp_ind(data_2006, FUAs, "2006")
CI_2011 <- Comp_ind(data_2011, FUAs, "2011")
CI_2016 <- Comp_ind(data_2016, FUAs, "2016")




library(ggplot2)
library(reshape2)

#run the function to produce plots
plots_2001 <- FUA_decile_plot(CI_2001$Comp_ind, "2001")
plots_2006 <- FUA_decile_plot(CI_2006$Comp_ind, "2006")
plots_2011 <- FUA_decile_plot(CI_2011$Comp_ind, "2011")
plots_2016 <- FUA_decile_plot(CI_2016$Comp_ind, "2016") 
```

## Calculate the difference in variables between 2016 and 2001

For all the variables I calculate % difference but for the index score the absolute difference
```{r}

data_2016_needed <- plots_2016$Grids_deciles[,c("ID", "Cmp_rnk_deciles", "GreenSp_deciles", "Wlkb_rnk_deciles", "built_index_rank_deciles")]

data_2011_needed <- plots_2011$Grids_deciles[,c("ID", "Cmp_rnk_deciles", "GreenSp_deciles", "Wlkb_rnk_deciles", "built_index_rank_deciles")]

data_2006_needed <- plots_2006$Grids_deciles[,c("ID", "Cmp_rnk_deciles", "GreenSp_deciles", "Wlkb_rnk_deciles", "built_index_rank_deciles")]

data_2001_needed <- plots_2001$Grids_deciles[,c("ID", "Cmp_rnk_deciles", "GreenSp_deciles", "Wlkb_rnk_deciles", "built_index_rank_deciles")]


```



```{r}
combined_01_16 <- left_join(data_2016_needed, data_2001_needed, by = "ID")
combined_01_16$diff01_16_decile <- combined_01_16$built_index_rank_deciles.x - combined_01_16$built_index_rank_deciles.y
combined_01_16$diff01_16_decile_compact <- combined_01_16$Cmp_rnk_deciles.x - combined_01_16$Cmp_rnk_deciles.y
combined_01_16$diff01_16_decile_grsp <- combined_01_16$GreenSp_deciles.x - combined_01_16$GreenSp_deciles.y
combined_01_16$diff01_16_decile_wlk <- combined_01_16$Wlkb_rnk_deciles.x - combined_01_16$Wlkb_rnk_deciles.y

cols <- c("ID", "diff01_16_decile", "diff01_16_decile_compact", "diff01_16_decile_grsp", "diff01_16_decile_wlk")

combined_01_16 <-  combined_01_16[,cols]
```


```{r}
combined_01_06 <- left_join(data_2006_needed, data_2001_needed, by = "ID")
combined_01_06$diff01_06_decile <- combined_01_06$built_index_rank_deciles.x - combined_01_06$built_index_rank_deciles.y
combined_01_06$diff01_06_decile_compact <- combined_01_06$Cmp_rnk_deciles.x - combined_01_06$Cmp_rnk_deciles.y
combined_01_06$diff01_06_decile_grsp <- combined_01_06$GreenSp_deciles.x - combined_01_06$GreenSp_deciles.y
combined_01_06$diff01_06_decile_wlk <- combined_01_06$Wlkb_rnk_deciles.x - combined_01_06$Wlkb_rnk_deciles.y

cols <- c("ID", "diff01_06_decile", "diff01_06_decile_compact", "diff01_06_decile_grsp", "diff01_06_decile_wlk")

combined_01_06 <-  combined_01_06[,cols]
```

```{r}
combined_06_11 <- left_join(data_2011_needed, data_2006_needed, by = "ID")
combined_06_11$diff06_11_decile <- combined_06_11$built_index_rank_deciles.x - combined_06_11$built_index_rank_deciles.y
combined_06_11$diff06_11_decile_compact <- combined_06_11$Cmp_rnk_deciles.x - combined_06_11$Cmp_rnk_deciles.y
combined_06_11$diff06_11_decile_grsp <- combined_06_11$GreenSp_deciles.x - combined_06_11$GreenSp_deciles.y
combined_06_11$diff06_11_decile_wlk <- combined_06_11$Wlkb_rnk_deciles.x - combined_06_11$Wlkb_rnk_deciles.y

cols <- c("ID", "diff06_11_decile", "diff06_11_decile_compact", "diff06_11_decile_grsp", "diff06_11_decile_wlk")

combined_06_11 <-  combined_06_11[,cols]
```


```{r}
combined_11_16 <- left_join(data_2016_needed, data_2011_needed, by = "ID")
combined_11_16$diff11_16_decile <- combined_11_16$built_index_rank_deciles.x - combined_11_16$built_index_rank_deciles.y
combined_11_16$diff11_16_decile_compact <- combined_11_16$Cmp_rnk_deciles.x - combined_11_16$Cmp_rnk_deciles.y
combined_11_16$diff11_16_decile_grsp <- combined_11_16$GreenSp_deciles.x - combined_11_16$GreenSp_deciles.y
combined_11_16$diff11_16_decile_wlk <- combined_11_16$Wlkb_rnk_deciles.x - combined_11_16$Wlkb_rnk_deciles.y

cols <- c("ID", "diff11_16_decile", "diff11_16_decile_compact", "diff11_16_decile_grsp", "diff11_16_decile_wlk")

combined_11_16 <-  combined_11_16[,cols]
```



```{r}
all_years <- left_join(combined_01_16, combined_01_06, by = "ID")
all_years <- left_join(all_years, combined_06_11, by = "ID")
all_years <- left_join(all_years, combined_11_16, by = "ID")
str(all_years)
```


# In this section is for creating cluster analysis for the grids that moved up or down one or more deciles in the composite index ranking from 2001 to 2016


```{r}

set1 <- subset(all_years, diff01_16_decile >= 1)
set2 <- subset(all_years, diff01_16_decile <= -1)


quantile(set1$diff01_16_decile, prob = seq(0, 1, length = 11), type = 5)
quantile(set2$diff01_16_decile, prob = seq(0, 1, length = 11), type = 5)

nrow(set1)
nrow(set2)
```

I select the top 10% of the changes for those who changes either positively or negatively.
For the ones moved down in decile from 1865 grids I selected 258
For the ones moved up in decile from 2401 grids I selected 306

```{r}
# subset the grids that increased or decreased in the ranking 
combined_01_16_subset1 <- subset(all_years, diff01_16_decile >= 4)
combined_01_16_subset2 <- subset(all_years, diff01_16_decile <= -3)


library(tidyr)
combined_01_16_subset1 <-combined_01_16_subset1 %>% 
  drop_na()

combined_01_16_subset2 <-combined_01_16_subset2 %>% 
  drop_na()

```




## This part is for the grids that moved down 4 or more deciles in the ranking

```{r}
df <- combined_01_16_subset1

library(cluster)

library(factoextra)
set.seed(123)
fviz_nbclust(df[-1], kmeans, method = "wss")
fviz_nbclust(df[-1], kmeans, method = "silhouette")


# Compute k-means clustering with k = 4
set.seed(123)
final <- kmeans(df[-1], 4, nstart = 25, iter.max = 1000)

fviz_cluster(final, data = df[-1])
```



```{r}
# summarise clusters
library(tidyverse)
cl_median <- df[-1] %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("median")


cl_mean <- df[-1] %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")


cl_sd <- df[-1] %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("sd")

```



```{r}
#convert the summary tables from long to wide format
library(tidyr)

median_down <- gather(cl_median, variable, median, diff01_16_decile:diff11_16_decile_wlk, factor_key=TRUE)
mean_down <- gather(cl_mean, variable, mean, diff01_16_decile:diff11_16_decile_wlk, factor_key=TRUE)
sd_down <- gather(cl_sd, variable, sd, diff01_16_decile:diff11_16_decile_wlk, factor_key=TRUE)

# combine them all in one dataframe
down_summary <- cbind(median_down, mean_down[,3], sd_down[,3])


# rename the variables
# I used levels as it is a factor, which helps to order the plot
levels(median_down$variable)[levels(median_down$variable)=="diff01_16_decile"] <- "SUDI 2016-2001"
levels(median_down$variable)[levels(median_down$variable)=="diff01_16_decile_compact"] <- "Compactness Domain 2016-2001"
levels(median_down$variable)[levels(median_down$variable)=="diff01_16_decile_grsp"] <- "Green/Open Space Domain 2016-2001"
levels(median_down$variable)[levels(median_down$variable)=="diff01_16_decile_wlk"] <- "Walkability Domain 2016-2001"

levels(median_down$variable)[levels(median_down$variable)=="diff01_06_decile"] <- "SUDI 2006-2001"
levels(median_down$variable)[levels(median_down$variable)=="diff01_06_decile_compact"] <- "Compactness Domain 2006-2001"
levels(median_down$variable)[levels(median_down$variable)=="diff01_06_decile_grsp"] <- "Green/Open Space Domain 2006-2001"
levels(median_down$variable)[levels(median_down$variable)=="diff01_06_decile_wlk"] <- "Walkability Domain 2006-2001"

levels(median_down$variable)[levels(median_down$variable)=="diff06_11_decile"] <- "SUDI 2011-2006"
levels(median_down$variable)[levels(median_down$variable)=="diff06_11_decile_compact"] <- "Compactness Domain 2011-2006"
levels(median_down$variable)[levels(median_down$variable)=="diff06_11_decile_grsp"] <- "Green/Open Space Domain 2011-2006"
levels(median_down$variable)[levels(median_down$variable)=="diff06_11_decile_wlk"] <- "Walkability Domain 2011-2006"

levels(median_down$variable)[levels(median_down$variable)=="diff11_16_decile"] <- "SUDI 2016-2011"
levels(median_down$variable)[levels(median_down$variable)=="diff11_16_decile_compact"] <- "Compactness Domain 2016-2011"
levels(median_down$variable)[levels(median_down$variable)=="diff11_16_decile_grsp"] <- "Green/Open Space Domain 2016-2011"
levels(median_down$variable)[levels(median_down$variable)=="diff11_16_decile_wlk"] <- "Walkability Domain 2016-2011"

# I create the plot further down the code


```




```{r}
# add an extra column indicating the cluster
df_temp_cl <- df %>%
  mutate(Cluster = final$cluster)

# count points by cluster
df_temp_cl %>% 
  count(Cluster)

```

```{r}
library(dplyr)
df_temp_cl_geo <- left_join(CI_2001$Domains_rank[,c("ID")], df_temp_cl, by = "ID")

library(tidyr)
df_temp_cl_geo <- df_temp_cl_geo %>% 
  drop_na(Cluster)


```




```{r}
library(tmap)
tmap_mode("view")

map1 <- tm_shape(df_temp_cl_geo) +
  tm_fill("Cluster", style = "cat", 
          palette = "Set1",
          alpha = 0.7, title = 'Clusters for grids moved down in SUDI ranking',
          showNA = FALSE,
          legend.hist = TRUE,
          labels = c("D1", "D2", "D3","D4")) +
  tm_basemap("CartoDB.DarkMatter")

tmap_save(map1,
          width = 1500, height = 1500,
          dpi = 300, filename = "../outputs/Clusters for grids moved down in SUDI ranking.html")
```


Plot an inset map
```{r}
# specify the crs
WGS84 = "+init=epsg:4326"
# transform the geospatial file to wgs84
df_temp_cl_geoWGS <- st_transform(df_temp_cl_geo,WGS84)


library(tmaptools)
library(raster)
# identify the bbox for the inset map showing the Ferguslie park
bb_select <- bb(extent(-4.479933,-4.425001,55.832545,55.858216), projection = WGS84)




```

```{r}
library("OpenStreetMap")
tile_1 <- read_osm(bb_select, ext=1.1)

```


```{r}

tmap_mode("plot")
Ferguslie_map <- tm_shape(tile_1) +
  tm_rgb()+
  tm_shape(df_temp_cl_geoWGS, bbox = bb_select) +
  tm_fill("Cluster", style = "cat", 
          palette = "Set1",
          alpha = 0.7, title = '',
          showNA = FALSE,legend.show = TRUE,
          labels = c("D1", "D2", "D3","D4")) +
  tm_layout(fontfamily = 'Avenir Next Condensed',
            legend.text.color = "black",
            legend.text.size = 1,
            main.title = "B. Ferguslie Park-Glasgow",
            title.size = 1,
            title.bg.color = TRUE,
            legend.position = c("right","top"))


png("../outputs/Ferguslie_map.png",units="in", width=15, height=10, res=300)
Ferguslie_map
dev.off() # Close the file


```




## This part is for the grids that moved up 3 or more deciles in the ranking

```{r}
df <- combined_01_16_subset2

library(cluster)

library(factoextra)
set.seed(123)
fviz_nbclust(df[-1], kmeans, method = "wss")
fviz_nbclust(df[-1], kmeans, method = "silhouette")


# Compute k-means clustering with k = 4
set.seed(123)
final <- kmeans(df[-1], 4, nstart = 25, iter.max = 1000)

fviz_cluster(final, data = df[-1])
```



```{r}
# summarise clusters
library(tidyverse)
cl_median <- df[-1] %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("median")


cl_mean <- df[-1] %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")


cl_sd <- df[-1] %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("sd")

```



```{r}
#convert the summary tables from long to wide format
library(tidyr)

median_up <- gather(cl_median, variable, median, diff01_16_decile:diff11_16_decile_wlk, factor_key=TRUE)
mean_up <- gather(cl_mean, variable, mean, diff01_16_decile:diff11_16_decile_wlk, factor_key=TRUE)
sd_up <- gather(cl_sd, variable, sd, diff01_16_decile:diff11_16_decile_wlk, factor_key=TRUE)

# combine them all in one dataframe
up_summary <- cbind(median_up, mean_up[,3], sd_up[,3])


# rename the variables
# I used levels as it is a factor, which helps to order the plot
levels(median_up$variable)[levels(median_up$variable)=="diff01_16_decile"] <- "SUDI 2016-2001"
levels(median_up$variable)[levels(median_up$variable)=="diff01_16_decile_compact"] <- "Compactness Domain 2016-2001"
levels(median_up$variable)[levels(median_up$variable)=="diff01_16_decile_grsp"] <- "Green/Open Space Domain 2016-2001"
levels(median_up$variable)[levels(median_up$variable)=="diff01_16_decile_wlk"] <- "Walkability Domain 2016-2001"

levels(median_up$variable)[levels(median_up$variable)=="diff01_06_decile"] <- "SUDI 2006-2001"
levels(median_up$variable)[levels(median_up$variable)=="diff01_06_decile_compact"] <- "Compactness Domain 2006-2001"
levels(median_up$variable)[levels(median_up$variable)=="diff01_06_decile_grsp"] <- "Green/Open Space Domain 2006-2001"
levels(median_up$variable)[levels(median_up$variable)=="diff01_06_decile_wlk"] <- "Walkability Domain 2006-2001"

levels(median_up$variable)[levels(median_up$variable)=="diff06_11_decile"] <- "SUDI 2011-2006"
levels(median_up$variable)[levels(median_up$variable)=="diff06_11_decile_compact"] <- "Compactness Domain 2011-2006"
levels(median_up$variable)[levels(median_up$variable)=="diff06_11_decile_grsp"] <- "Green/Open Space Domain 2011-2006"
levels(median_up$variable)[levels(median_up$variable)=="diff06_11_decile_wlk"] <- "Walkability Domain 2011-2006"

levels(median_up$variable)[levels(median_up$variable)=="diff11_16_decile"] <- "SUDI 2016-2011"
levels(median_up$variable)[levels(median_up$variable)=="diff11_16_decile_compact"] <- "Compactness Domain 2016-2011"
levels(median_up$variable)[levels(median_up$variable)=="diff11_16_decile_grsp"] <- "Green/Open Space Domain 2016-2011"
levels(median_up$variable)[levels(median_up$variable)=="diff11_16_decile_wlk"] <- "Walkability Domain 2016-2011"





```




```{r}
# I combine the two datasets so I can use facet wrap
median_down2 <- median_down
median_down2$direction <- "Decrease"
median_down2$Cluster[median_down2$Cluster==1] <- "D1 (n=66)"
median_down2$Cluster[median_down2$Cluster==2] <- "D2 (n=35)"
median_down2$Cluster[median_down2$Cluster==3] <- "D3 (n=72)"
median_down2$Cluster[median_down2$Cluster==4] <- "D4 (n=61)"

median_up2 <- median_up
median_up2$direction <- "Increase"
median_up2$Cluster[median_up2$Cluster==1] <- "U1 (n=38)"
median_up2$Cluster[median_up2$Cluster==2] <- "U2 (n=66)"
median_up2$Cluster[median_up2$Cluster==3] <- "U3 (n=61)"
median_up2$Cluster[median_up2$Cluster==4] <- "U4 (n=139)"

combined <- rbind(median_down2, median_up2)
combined$median <- round(combined$median, 0)


library(viridis)
library(grid)

plot2 <- ggplot(combined, aes(Cluster, variable, fill= median)) + 
  geom_tile() +
  geom_text(aes(label=median), family="Arial", fontface='bold', colour = "grey60", size = 2) + # fontface='bold'
  scale_fill_viridis(option="magma", limits = c(min(median_up$median),max(median_down$median)), direction = -1) +
  #scale_fill_gradient(limits = c(min(median_up$median),max(median_down$median)), low="#eae2b7", high="#003049") + # I specify the range to be the same in the two plots so they use the same colours
  scale_y_discrete(limits = rev(levels(combined$variable)),
                   labels=c("SUDI 2016-2001"="SUDI",
                            "Compactness Domain 2016-2001"="Compactness Domain", 
                            "Green/Open Space Domain 2016-2001"="Green/Open Space Domain",
                            "Walkability Domain 2016-2001"="Walkability Domain",
                            "SUDI 2006-2001"="SUDI",
                            "Compactness Domain 2006-2001"="Compactness Domain", 
                            "Green/Open Space Domain 2006-2001"="Green/Open Space Domain",
                            "Walkability Domain 2006-2001"="Walkability Domain",
                            "SUDI 2011-2006"="SUDI",
                            "Compactness Domain 2011-2006"="Compactness Domain", 
                            "Green/Open Space Domain 2011-2006"="Green/Open Space Domain",
                            "Walkability Domain 2011-2006"="Walkability Domain",
                            "SUDI 2016-2011"="SUDI",
                            "Compactness Domain 2016-2011"="Compactness Domain", 
                            "Green/Open Space Domain 2016-2011"="Green/Open Space Domain",
                            "Walkability Domain 2016-2011"="Walkability Domain")) +
  #ylim(rev(levels(median_up$variable))) +
  theme_minimal() +
  labs(x="",
       y="") +
  theme(
      text = element_text('Arial'),
      axis.text.x=element_text(angle = 45, hjust = 1, size=8),
      axis.text.y=element_text(size=8),
      strip.text = element_text(hjust = 0, size = 10),
      plot.caption = element_text(face = 'italic'),
      panel.grid.minor = element_blank(),
      legend.position = "none",
      plot.margin = unit(c(1,1,1,1), "cm"),
      aspect.ratio = 2 # this line plays around with the size of the grids, if I put 0.5 width is larger
      ) +
  #coord_equal() +
  geom_hline(yintercept=4.5) +
  geom_hline(yintercept=8.5) +
  geom_hline(yintercept=12.5) +
  facet_wrap(~direction, scales = "free_x")

# create a dataframe just to store the annotation to be used
ann_text <- data.frame(x = c(0.1,0.1,0.1,0.1),y = c(14.5, 10.5, 6.5, 2.5),
                       lab = c("2016-2001", "2006-2001", "2011-2006", "2016-2011"),Cluster=c("test", "test", "test", "test"),
                       variable=c("test", "test", "test", "test"),
                       median=c(6,6,6,6),
                       direction = factor(c("Decrease","Decrease","Decrease","Decrease"),levels = c("Increase","Decrease")))



plot2 + geom_text(data = ann_text, aes(x=x,y=y,label = lab, vjust = 1), angle = 90,
                  family="Arial",fontface='bold', size = 2)

final_plot <- plot2 + geom_text(data = ann_text, aes(x=x,y=y,label = lab, vjust = 1), angle = 90,
                  family="Arial",fontface='bold', size = 2)


#png("testing_facets.png", width=1000, height=500, res=1000) # Open a new png file
png("../outputs/cluster_summary_plot.png",units="in", width=5, height=4, res=300)
final_plot
dev.off() # Close the file

```


```{r}
# add an extra column indicating the cluster
df_temp_cl <- df %>%
  mutate(Cluster = final$cluster)

# count points by cluster
df_temp_cl %>% 
  count(Cluster)

```

```{r}
library(dplyr)
df_temp_cl_geo2 <- left_join(CI_2001$Domains_rank[,c("ID")], df_temp_cl, by = "ID")

library(tidyr)
df_temp_cl_geo2 <- df_temp_cl_geo2 %>% 
  drop_na(Cluster)


```


```{r}
library(tmap)
tmap_mode("view")

map2 <- tm_shape(df_temp_cl_geo2) +
  tm_fill("Cluster", style = "cat", 
          palette = "Set1",
          alpha = 0.7, title = 'Clusters for grids moved up in SUDI ranking',
          showNA = FALSE,
          legend.hist = TRUE,
          labels = c("U1", "U2", "U3","U4")) +
  tm_basemap("CartoDB.DarkMatter")


tmap_save(map2,
          width = 1500, height = 1500,
          dpi = 300, filename = "../outputs/Clusters for grids moved up in SUDI ranking.html")
```


Plot a second inset map
```{r}
df_temp_cl_geo_2WGS <- st_transform(df_temp_cl_geo2,WGS84)

# identify the bbox for the inset map showing the Olympic park
bb_select2 <- bb(extent(-0.045319,0.014420,51.528186,51.560623), projection = WGS84)

```



```{r}
tile_2 <- read_osm(bb_select2, ext=1.1, type = "osm")

```




```{r}

tmap_mode("plot")
OlympicPark_map <- tm_shape(tile_2) +
  tm_rgb()+
  tm_shape(df_temp_cl_geo_2WGS, bbox = bb_select2) +
  tm_fill("Cluster", style = "cat", 
          palette = "Set1",
          alpha = 0.7, title = '',
          showNA = FALSE,legend.show = TRUE,
          labels = c("U1", "U2", "U3","U4")) +
  tm_layout(fontfamily = 'Avenir Next Condensed',
            legend.text.color = "black",
            legend.text.size = 1,
            main.title = "A. Olympic Park-Stratford",
            title.size = 1,
            title.bg.color = TRUE,
            legend.position = c("right","top"))


png("../outputs/OlympicPark_map.png",units="in", width=15, height=10, res=300)
OlympicPark_map
dev.off() # Close the file


```


```{r}

# put the two inset maps together
png("../outputs/two_inset_maps.png",units="in", width=10, height=5, res=300)
tmap_arrange(OlympicPark_map, Ferguslie_map, ncol = 2)
dev.off() #

```






